---
title: 'Chapter 2 #6'
author: "Bonnie Romeo"


output: word_document
---

```{r setup, include=FALSE}
library(ma391romeo)
library(MASS)
library(NlcOptim)
```

A)

```{r, warning=FALSE, error = FALSE}
P = function(x){return((10000+(950-x[1])*((0.5)/100)*10000)+(x[2]-5000*(200/10000))*(-1))}
```

This is not evaluated as it ran, but when tried to knit, would tell me there is an as.vector error
```{r, eval = FALSE}
x=c(2,400)
dP = function(x){fprime(P,x)}
dP

dP(x)

###Linear Inequality Constraints##
x0=c(1000,1000)
Aeq = matrix(c(1,0,0,1),nrow=2) 
Beq = matrix(c(0,10000),nrow=2)
print(Aeq)
print(Beq)
ans=solnl(x0,objfun=P,A=A,B=B)
print(ans$lambda)
```

```{r}
obj=function(x){((10000*(1+0.5*x[1]))+200*x[2])*(950-100*x[1])-(700*(10000*(1+0.5*x[1])+200*x[2]))-(50000-10000*x[2])*-1}

con=function(x){
  f=NULL
  f=rbind(f,-50000-10000*x[1])
  return(list(ceq=f,c=NULL))
}
x0=c(1,1)
ans=solnl(x0,obj=obj,con=con)
```
I tried two ways as I was unable to get an answer that i was pleased with

B) If I were to do this problem I would change the price elasticity by changing the 0.5 value to a variable. I would then conduct sensitivity analysis which runs through the different prices when it varies from 25% to 75%. 

C)If I were to do this problem i would replace the (200/10000)  with an R variable, first on each individual aspect and then on the whole number to see the different results/ 


