---
title: "LSN09"
author: "Bonnie Romeo"

output: word_document
---

```{r setup, include=FALSE}
library(ma391romeo)
library(MASS)
library(NlcOptim)
```

Problem 1 (Equality Constraints)
maxx1,x2x1(600−3x1+x2)+x2(800−2x2+x1) 
s.t. 12x1+5x2=2500 

```{r}
obj = function(x){((600-3*x[1]+x[2])*x[1]+(800-2*x[2]+x[1])*x[2])*-1}
Aeq = matrix(c(12, 5), nrow =1, byrow = TRUE)
Beq = matrix(c(2500), nrow = 1, byrow = TRUE)

x0 = c(0,500)
ans = solnl(x0, obj = obj, Aeq = Aeq, Beq = Beq)

print(ans$par)
```

```{r}
f = function(x){x[1]^2+x[2]^2}
Aeq = matrix(c(1,2),nrow=1)
Beq = matrix(5)
x0=c(5,0)
ans = solnl(x0,f,Aeq=Aeq,Beq=Beq)
print(ans)
```


Problem 2 (Inequality Constraints)
maxx1,x2x1(600−3x1+x2)+x2(800−2x2+x1) 
s.t. 12x1+5x2≤2500 
x1≥0 
x2≥0 

```{r}

A = matrix(c(12, 5, -1, 0, 0, -1), nrow = 3, byrow = TRUE)
B = matrix(c(2500, 0, 0), nrow = 3)

obj = function(x){((600-3*x[1]+x[2])*x[1]+(800-2*x[2]+x[1])*x[2])*-1}
X = list(x=seq(0,500),y=seq(0,500))
ans = solnl(x0,objfun = obj,A=A,B=B)
print(ans$par)
```


Problem 3: Explain why did prob1,2 give the same solution and we got different answers in the two sections above?

They gave the same solution because it looks to maximize, thus, typically would be nonnegative anyways. 

Problem 4: Create a contour plot with constraints for problems 1,2.

```{r}
obj = function(x){((600-3*x[1]+x[2])*x[1]+(800-2*x[2]+x[1])*x[2])*(-1)}
X = list(x=seq(0,500),y=seq(0,500))
Z = Outer(obj,X)
contour(X$x,X$y,-Z)

```


Problem 5
maxx,yx(10+22x−0.5+1.3y−0.1)−18x+y(5+15y−0.5+0.8x−0.08)−10y 

```{r}
f=function(x){((10+22*x[1]^(-0.5)+1.3*x[2]^(-0.1))-18*x[1]+x[2]*(5+15*x[2]^(-0.5)+0.8*x[1]^(-0.08))-10*x[2])*(-1)}

#I am not sure if I types obj wrong, as I was getting an error message when I tried to optim. 
x = c(100,100)
ans = optim(x,f)
print(ans)
```

Problem 6 - Find the solution and plot the contour of the objective unction, the constraints and the solution.
maxx,yx(10+22x−0.5+1.3y−0.1)−18x+y(5+15y−0.5+0.8x−0.08)−10y 
s.t. 2x+3y≤18 
x≥3 
y≥2 

```{r}
obj=function(x){((10+22*x[1]^(-0.5)+1.3*x[2]^(-0.1))-18*x[1]+x[2]*(5+15*x[2]^(-0.5)+0.8*x[1]^(-0.08))-10*x[2])*(-1)}
X = list(x=seq(0,500),y=seq(0,500))
Z = Outer(obj,X)
contour(X$x,X$y,-Z)
#This graph does not look right 
```

```{r,eval = FALSE}
obj= function(x){((10+22*x[1]^(-0.5)+1.3*x[2]^(-0.1))-18*x[1]+x[2]*(5+15*x[2]^(-0.5)+0.8*x[1]^(-0.08))-10*x[2])*(-1)}
A = matrix(c(2,3,-1,0,0,-1), nrow =3, byrow = TRUE)
B = matrix(c(18,3,2), nrow = 3)

X = list(x=seq(0,500),y=seq(0,500))
x0 = c(100,100)
#Getting an error here 
ans = solnl(x0,obj = obj,A=A,B=B)
print(ans$par)
```


Problem 7 - Find the solution and plot the contour of the objective unction, the constraints and the solution.
maxx,yx(10+22x−0.5+1.3y−0.1)−18x+y(5+15y−0.5+0.8x−0.08)−10y 
s.t. 50x+100y≥600 
x≤7 
y≤5 

NOTE: My solnl is not running/updating my ans. I belive it is printing out the previous ans input that it recieved. 
```{r}
obj=function(x){((10+22*x[1]^(-0.5)+1.3*x[2]^(-0.1))-18*x[1]+x[2]*(5+15*x[2]^(-0.5)+0.8*x[1]^(-0.08))-10*x[2])*(-1)}
A = matrix(c(50,100,1,0,0,1),nrow=3,byrow=T)
B = matrix(c(600,5,7),nrow=3)
print(A)
print(B)
```

```{r}
X = list(x=seq(0,500),y=seq(0,500))
Z = Outer(obj,X)
contour(X$x,X$y,Z)
```

```{r, eval = FALSE}
ans = solnl(X, obj = obj,A=A,B=B)
print(ans)
```


Problem 8 - Find the solution (you will need to define A,B, Aeq, and Beq for this one).
maxx,yx(10+22x−0.5+1.3y−0.1)−18x+y(5+15y−0.5+0.8x−0.08)−10y 
s.t. 2x+3y+s1=18 
−x+s2=3 
−y+s3=2 
s1≥0 
s2≥0 
s3≥0

```{r}
obj=function(x){((10+22*x[1]^(-0.5)+1.3*x[2]^(-0.1))-18*x[1]+x[2]*(5+15*x[2]^(-0.5)+0.8*x[1]^(-0.08))-10*x[2])*(-1)}
Aeq = matrix(c(2,3,1,-1,0,0,1,0,-1,0,0,1), nrow = 3, byrow = TRUE)
Beq = matrix(c(18,3,2), nrow = 3, byrow = TRUE)
A = matrix(c(1,0,0,0,1,0,0,0,1), nrow = 3, byrow = TRUE)
B = matrix(c(0,0,0), nrow = 3, byrow = TRUE)
```

